---
title: fastTextR - Word representations
output: html_document
vignette: >
  %\VignetteIndexEntry{Word_representations}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

**fastTextR** is an **R** interface to the [fastText](https://github.com/facebookresearch/fastText)
library. It can be used to **word representation learning** *(Bojanowski et al., 2016)* and 
**supervised text classification** *(Joulin et al., 2016)*.
Particularly the advantage of **fastText** to other software is that, 
it was designed for biggish data.

The following example is based on the examples provided in the **fastText** library, 
the example shows how to use **fastTextR** for word representation.
For more informations about word representations can be found at the
[fastText  homepage](https://fasttext.cc/docs/en/unsupervised-tutorial.html).
```{r}
library("fastTextR")
```


## Load pretrained model
The training of these models can be quite time consuming therefore pre-trained 
models are a good option.
```{r, load}
model <- ft_load("cc.en.300.bin")
```

## Printing word vectors
```{r, print}
ft_word_vectors(model, c("asparagus", "pidgey", "yellow"))[,1:5]
```

## Nearest neighbor queries
```{r, neighbor_queries}
ft_nearest_neighbors(model, 'asparagus', k = 5L)
```

## Word analogies
```{r, analogies}
ft_analogies(model, c("berlin", "germany", "france"))
```


## References

[1] P. Bojanowski, E. Grave, A. Joulin, T. Mikolov, [*Enriching Word Vectors with Subword Information*](https://arxiv.org/abs/1607.04606)

```
@article{bojanowski2016enriching,
  title={Enriching Word Vectors with Subword Information},
  author={Bojanowski, Piotr and Grave, Edouard and Joulin, Armand and Mikolov, Tomas},
  journal={arXiv preprint arXiv:1607.04606},
  year={2016}
}
```

[2] A. Joulin, E. Grave, P. Bojanowski, T. Mikolov, [*Bag of Tricks for Efficient Text Classification*](https://arxiv.org/abs/1607.01759)

```
@article{joulin2016bag,
  title={Bag of Tricks for Efficient Text Classification},
  author={Joulin, Armand and Grave, Edouard and Bojanowski, Piotr and Mikolov, Tomas},
  journal={arXiv preprint arXiv:1607.01759},
  year={2016}
}
```
